Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging Patterns of Queen Bumble Bees

### 2023-02-26 script/manuscript_MEE.Rmd
importing final data for comparisions

```{r Build reference dataset for reclassification process}
reclassified <- read.csv('../data/Fully_Integrated_Corbiculae.csv')
```

>>>>

```{r compare results}

blast <- read.csv('../data/tally_blast_classifications.csv') %>% 
  group_by(Sample) %>% 
  slice_max(Prcnt_seqs, n = 10) %>% 
  select(Sample, Taxon = taxid, Percent_Sample = Prcnt_seqs) %>% 
  mutate(
    Taxon = str_replace(Taxon, 'Arenaria', 'Eremogone'),
    Genus = str_remove(str_extract(Taxon, '^.* '), ' '),
    Method = 'BLAST')

automated <- read.csv('../data/Post_Classified_BLAST_sqs.csv') %>% 
  group_by(Sample, TAXON_NEW) %>%
  mutate(Prcnt_seqs = sum(Prcnt_seqs)) %>% 
  drop_na() %>% 
  distinct(Sample, TAXON_NEW, .keep_all = T) %>% 
  ungroup(TAXON_NEW) %>% 
  slice_max(Prcnt_seqs, n = 10) %>% 
  select(Sample, Genus = GENUS, Taxon = TAXON_NEW, Percent_Sample = Prcnt_seqs) %>% 
  mutate(across(where(is.character), ~ str_replace(., 'Arenaria', 'Eremogone')),
         Method = 'Automated')

expert <- read.csv('../data/Fully_Integrated_Corbiculae.csv') %>% 
  rename(Sample = sample.id) %>% 
  mutate(across(where(is.character), ~ str_trim(.)), 
         Method = 'Expert') %>% 
  drop_na() %>% 
  relocate()

genera2query <- na.omit(unique(c(blast$Genus, automated$Genus, expert$Genus))) 
genera2query <- genera2query[genera2query != 'Ericaceae'] 
genera2query <- taxizedb::name2taxid(genera2query, out_type = 'summary')

genera_out <- taxizedb::classification(genera2query$id, db='ncbi', rank = 'family') 
genera_out <- map(genera_out, ~ 
                    data.frame( 
                      'Family' = filter(.x, rank == "family") %>% select(name), 
                      'Genus' = filter(.x, rank == 'genus') %>%  select(name) 
                      )) %>% 
  bind_rows() %>% 
  rename(Family = 1, Genus = 2)

all_classifications <- bind_rows(
  automated, blast, expert
) %>% 
  left_join(., genera_out, by = 'Genus') %>% 
  mutate(Rank = case_when(
    is.na(Family) ~ 'Family',
    Taxon == Family ~ 'Family',
    Taxon == Genus ~ 'Genus',
    TRUE ~ 'Species'
  ),
  Family = if_else(Taxon == 'Ericaceae', 'Eriaceae', Family))

rm(genera2query, genera_out, automated, blast, expert)
```
